DOpElib: Differential Equations and Optimization Environment; A Goal Oriented Software Library for Solving PDEs and Optimization Problems

### 2012-11-27 Paper_May_2012/main.tex
Aenderungen und Kommentare von cg ab 2.2 bis zum Ende, hatte nicht gespeichert

This means for the user only the derivatives of the functional and the PDE 
needs to be provided in addition to the 
\begin{lstlisting} 
  void CellEquation_U(...)
   {
     // implement directional derivative 
     // of the CellEquation
   }
\end{lstlisting}
and functional terms, i.e.,     
\begin{lstlisting} 
  void BoundaryValue_U(...)
   {
     // implement here the derivative of 
     // the boundary cost functional
   }
\end{lstlisting}

>>>>

This means for the user only the derivatives of the functional and the PDE 
needs to be provided in addition to the  \todocg{Verstehe diesen Satz nicht. Das sind doch die Ableitungen des Funktionals und der PDE, warum addition?}
\begin{lstlisting} 
  void CellEquation_U(...)
   {
     // implement directional derivative 
     // of the CellEquation
   }
\end{lstlisting}
and functional terms, i.e.,     
\begin{lstlisting} 
  void BoundaryValue_U(...)
   {
     // implement here the derivative of 
     // the boundary cost functional
   }
\end{lstlisting}
